%-------------------------
% Resume in Latex
% Author : Mahima Sachan
% Website: https://github.com/mahima110298/Resume/new/main
% Reference: Sourabh Bajaj Resume (https://github.com/sb2nov/resume/blob/master/sourabh_bajaj_resume.tex)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\listItem}[1]{
  \item\small{{#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadingWithDescription}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-1pt}
    \small#5
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}
 
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeListItem}[1]{\listItem{#1}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Mahima Sachan} & Email : \href{mailto:mahimasachan@gmail.com}{\color{blue}mahimasachan@gmail.com}\\
  \href{https://www.linkedin.com/in/mahimasachan}{LinkedIn: \color{blue}mahimasachan} & Mobile : +91 - 72330 93831 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}

  \resumeSubHeadingListStart
    \resumeSubheadingWithDescription
      {Motilal Nehru National Institute of Technology}{Prayagraj, India}
      {B.Tech. in Computer Science and Engineering;  CGPA: 8.21/10}{July 2015 - May 2019}
      {Related coursework: Operating Systems, Distributed Systems, Database Systems, Object Oriented Modeling}
    \resumeSubheading
      {Kendriya Vidyalaya No - 1, Armapur}{Kanpur, India}
      {Class XII;  Percentage: 96.6\%}{Apr. 2014 - Jun. 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Microsoft}{Hyderabad, India}
      {Software Engineer I/II}{Dec. 2020 - Present}
      \resumeItemListStart
        \resumeItem{AI Graph}
          {AI Graph is a data-intensive service that processes and stores every email, meeting, and document any O365 user receives and makes that information accessible in $\sim$100 ms per request. I ingested data from various sources into the graph to support additional use cases. Currently working on minimizing memory usage for the service by analyzing heap traces and filtering out scopes for improvement. \textbf{[ML, C\#]}}
        \resumeItem{Voice access}
          {Voice access is an accessibility product that comes with Windows 11. I independently worked on the UI for the first run experience of voice access. Designed the UI to be scalable to different text sizes, screen sizes, and resolutions, supported contrast themes, and made it accessible by keyboard and screen readers. Collaborated with design and PM team. Resolved bugs from accessibility, craftsmanship reviews, and customers. \textbf{[XAML, C++/WinRT]}}
      \resumeItemListEnd

    \resumeSubheading
      {Salesforce}{Hyderabad, Inida}
      {AMTS/MTS}{Jun. 2019 - Dec. 2020}
      \resumeItemListStart
        \resumeItem{MTA API}
          {MTA API is a set of REST APIs which uses the existing sprocs to automate the manual workflow involved in using the UI. It also provides better guardrail over the existing functionality. This helped in $\sim$80\% savings in operations time i.e. reduction from 5 minutes to $\leq$ 1 minute per server. \textbf{[Go, Docker, Kubernetes]}}
        \resumeItem{Commvault Patching Tool}
          {The Commvault Patching Tool is a UI application backed by scripts which facilitates operations to be performed before and after patching through a simple click of a button. This automation eliminated manual involvement in patching from 5 engineer days to 0. \textbf{[Powershell]}}
        \resumeItem{SRMS in Europe Region}
          {Provided support for an in-house application(SRMS) in Europe Region respecting GDPR compliance. \textbf{[ASP.NET, C\#]}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Home Automation}
      {Home automation will control home appliances in manual and automatic mode as per user choice. Placed sensors like temperature, light and PIR to record conditions of surroundings. Algorithms can make decisions based on the data in automatic mode. User will always get to know the status of home appliances via an app. \textbf{[Raspberry Pi, Python]}}
    \resumeSubItem{News Classification}
      {Classification of news into 10 different categories. Comparison of classification using inbuilt Multinomial Naive Bayes and self-implemented Naive Bayes. Metric for comparison are classification report and confusion matrix. \textbf{[ML, Python]}}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills Summary}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}
      {C\#, C++, Java, SQL, Python, Go, Powershell, XAML, HTML, CSS, CSHTML}
    \resumeSubItem{Tools \& Technologies}
      {Visual studio, Git, Azure Dev Ops, WinRT, OData, Swagger, CI/CD, Unity 3D game engine, Docker, Kubernetes, Rest API, Micro services, ASP.NET}
 \resumeSubHeadingListEnd


%--------ACHIEVEMENTS------------
\section{Achievements}
 \resumeSubHeadingListStart
   \resumeListItem
      {3rd place in Microsoft's Global Hackathon'22 among  $\sim$800 candidates in Hyderbad, India}
   \resumeListItem
      {Received the Star Award for quality and artisanship from leaders at Windows India for my work in voice access.}
    \resumeListItem
      {Received spot bonus from the director of Marketing Cloud, Salesforce, India for demonstrating ownership and leadership.}
    \resumeListItem
      {Secured 99.74 percentile in JEE Mains among 1.5 million candidates}
 \resumeSubHeadingListEnd
 
 
%--------ACHIEVEMENTS------------
\section{Volunteer}
 \resumeSubHeadingListStart
   \resumeListItem
      {Organized meetups for engineering women in the Windows India group. It involved discussions on pressing topics surrounding women in tech.}
    \resumeListItem
      {Guided a group of young college students associated with Being Zero Pvt. Ltd. in their placements.}
 \resumeSubHeadingListEnd
 
 
%-------------------------------------------
\end{document}
